%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.275in}
\addtolength{\evensidemargin}{-0.275in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{0pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    { #2 \vspace{0pt}}
  }
}

\newcommand{\projectItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}
\newcommand{\projectSubItem}[2]{\projectItem{#1}{#2}\vspace{0pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.kelbykramer.com}{\Large Kelby Kramer}} & \href{http://www.kelbykramer.com}{http://www.kelbykramer.com}\\
  \href{mailto:kramerkelby@gmail.com}{kramerkelby@gmail.com} & \href{https://www.linkedin.com/in/kelby-kramer-472a0218b/}{LinkedIn} \\
  {Mobile : +1-307-871-0539} & \href{https://github.com/KelbyKramer}{GitHub} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Meta}{Menlo Park, CA}
      {Software Engineering Intern (Exceeds Expectations)}{May 2022 - Aug 2022}
      \resumeItemListStart
      \resumeItem{}
          { Designed optimal implementation solutions using RAFT strong consistency consensus algorithm across a distributed storage system that 
          scales to 3 billion active users for WhatsApp messages (100 billion/day).}
          \resumeItem{}
          { Added witness replica functionality to existing RAFT implementation using Erlang/OTP. Upon launch reduced network throughput by 
          95\%, CPU usage by 90\%, and memory usage by 85\%.}
          \resumeItem{}
          {  Gave a company-wide Tech Talk that presented project and key metrics to senior leadership.  Received Legendary Presenter Award for project
          presentation and impact.}
        \resumeItemListEnd

    \resumeSubheading
      {Hall of Fame Bets}{Remote}
      {Software Engineering Intern}{Nov 2022 - Present}
      \resumeItemListStart
        \resumeItem{}
          { Designed and implemented a custom parlay optimizer and deep stats analysis tool. Implementation allows for users to easily understand the odds of different parlays and outcomes for sporting events across the NBA and 
          NFL.}
        \resumeItem{}
          { Developed a fully custom responsive table library across the entire platform (Leaderboard, Deep Stats, and Parlay Optimizer) for viewing different statistical categories at custom user defined thresholds.
          }
      \resumeItemListEnd

    \resumeSubheading
      {Art of Velocity}{Remote}
      {Software Engineering Intern}{Aug 2022 - Nov 2022}
      \resumeItemListStart
        \resumeItem{}
          { Led implementation and deployment of a cross-platform mobile app’s fully custom and responsive game library. Games were developed using NodeJS, Vue, TypeScript, and React Native.
          }
        \resumeItem{}
          { Collaborated, wrote, and edited specifications and UI to produce games that target training reaction time, spatial awareness, memory, and other 
          cognitive functions for competitive athletes.}
      \resumeItemListEnd  
      \resumeSubheading
      {Minnesota Elevator Inc}{Mankato, MN}
      {Software Engineering Intern}{Nov 2020 - Aug 2021}
      \resumeItemListStart
        \resumeItem{Elevator Monitoring System:}
          {Designed, implemented, and oversaw the infrastructure and testing harness for a fully custom, real-time elevator monitoring system using 
          a full web stack (LAMP) along with a REST API. }
        \resumeItem{Elevator Monitoring System:}
          { Developed controller board testing software in C\# used across 4 elevator systems using RS-485 serial communication protocol for boards to be verified and tested before moving into production }
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \projectSubItem{GPT-3 Explain It Like I'm 5}
      {Search engine using GPT-3 API that allows users to receive instant tailor specified explanations on any subject imaginable}
    \projectSubItem{Semi-autonomous Duck Decoy}
      {Developed a client-facing web application that allows for fully customizable remote control of a duck decoy’s path. Designed and implemented real time navigation and tracking algorithm.}
    \projectSubItem{Reaction Lights}
      {Real time reaction lights simulator used by professional  and collegiate athletes.}
      \projectSubItem{Auomated Cat Litterbox}
      {Developed and launched firmware and touchscreen UI using Arduino Mega 2560}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \projectSubItem{Languages:}
  {Python, Javascript, PHP, Erlang, C\#, C/C++, SQL, Java}
  \projectSubItem{Technologies:}
  {React, Vue, NodeJS, jQuery, Arduino, React Native, Firebase}
  \projectSubItem{Skills:}
  {Distributed Computing, Full Stack Web Development, Game Development, Firmware Development, Agile Development}
 \resumeSubHeadingListEnd
 
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Minnesota State University}{Mankato, MN}
      {Bachelor of Science in Computer Engineering;  GPA: 3.71}{Aug. 2019 -- May. 2023}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}